Centralizers of higher enveloping algebras of Lie algebras

### 2020-09-03 draft.tex
swiss

@@

First, recall that an $L_\infty$ algebra $\fg$, with its collection of brackets $\{\ell_n\}_{n \geq 1}$ is fully encoded by its dg conilpotent cocommutative coalgebra
\[
\cliels(\fg) = (\Sym(\fg[1]), \d = \sum_n \ell_n)
\]
where the sum of the brackets provides a square-zero coderivation.
The square-zero condition efficiently encodes the higher Jacobi relations.
This coalgebra is canonically coaugmented by the inclusion of the base field $k \xto{\simeq} \Sym^0(\fg[1])$.
Let $\overline{\cliels(\fg)} \subset \cliels(\fg)$ denote the subcoalgebra given by the direct sum over positive symmetric powers of $\fg[1]$,
which can be identified with both the kernel of the counit map as well as cokernel of the coaugmentation map.

@@

An algebra over this colored operad can be identified with a pair of objects $(B,M)$ where $B$ is an $E_{n+1}$-algebra and $M$ is a left $B$-module. 
Indeed, if one restricts to the ``disk" colors we recover the data of $B$. 
The operadic structure maps which include disks and half-disks embedded inside bigger half-disks encodes the left-module structure of $A$ on $B$.

@@

Abstractly, an algebra over the $(n+1)$-dimensional Swiss cheese operad can be modeled as a {\em constructible} factorization algebra on the upper half space $\HH^{n+1}$. 
Concretely, this is the data of (1) a locally constant factorization algebra on the ``bulk" manifold $\RR^n \times \RR_{>0}$, (2) a locally constant factorization algebra on the boundary $\RR^n \times \{0\}$, (3) together with natural \brian{finish}

We have developed locally constant factorization models separately for enveloping $E_n$-algebras and their centers.
Combining these descriptions we obtain the following.

\begin{prp}
For any smooth manifold $M$ and Lie algebra $\fg$ the pair $(\bZ_n(\fg), \bU_n (\fg))$ define a constructible factorization algebra on the $(n+1)$-manifold with boundary $M \times \RR_{\geq 0}$.
When $M = \RR^n$, this is a model for the algebra $(\fZ_n(\fg), \UU_n(\fg))$ over the $(n+1)$-dimensional Swiss cheese operad.
\end{prp}

\begin{proof}[Proof sketch]
In the bulk manifold $M \times \RR_{>0}$ we place the 
\end{proof}

>>>>

\subsection{Comments on a generalization}

\owen{I think we can conjecture here the general statement that we almost proved and sketch an approach.}

@@

First, recall that an $L_\infty$ algebra $\fg$, with its collection of brackets $\{\ell_n\}_{n \geq 1}$ is fully encoded by its dg conilpotent cocommutative coalgebra
\[
\cliels(\fg) = \bigg(\Sym(\fg[1]) \; , \; \d = \sum_{n \geq 1} \ell_n\bigg)
\]
where the sum of the brackets provides a square-zero coderivation.
The square-zero condition efficiently encodes the higher Jacobi relations.
This coalgebra is canonically coaugmented by the inclusion of the base field $k \xto{\simeq} \Sym^0(\fg[1])$.
Let $\overline{\cliels(\fg)} \subset \cliels(\fg)$ denote the subcoalgebra given by the direct sum over positive symmetric powers of $\fg[1]$,
which can be identified with both the kernel of the counit map as well as cokernel of the coaugmentation map.

@@

An algebra over this colored operad can be identified with a pair of objects $(B,M)$ where $B$ is an $E_{n+1}$-algebra and $M$ is an $E_n$-algebra in the category of left $B$-modules.
Indeed, if one restricts to the ``disk" colors we recover the data of $B$. 
The operadic structure maps which include disks and half-disks embedded inside bigger half-disks encodes the left-module structure of $A$ on $B$.

@@

Abstractly, an algebra over the $(n+1)$-dimensional Swiss cheese operad can be modeled as a {\em constructible} factorization algebra on the upper half space $\HH^{n+1}$. 
Concretely, this is the data of a pair $(\bB, \bM)$ where $\bB$ is a locally constant factorization algebra on the ``bulk" manifold $\RR^n \times \RR_{>0}$ and $\bM$ is a locally constant factorization algebra on the boundary $\RR^n \times \{0\}$.

\begin{prp}[\cite{Lurie, AF}]
For any smooth manifold $M$ and Lie algebra $\fg$ there exists a constructible factorization algebra on $M \times \RR_{\geq 0}$ which is a model for the algebra $(\fZ_n(\fg), \UU_n(\fg))$ over the $(n+1)$-dimensional Swiss cheese operad.
\end{prp}

%We have developed locally constant factorization models separately for enveloping $E_n$-algebras and their centers.
%Combining these descriptions we obtain the following.
%
%\begin{prp}
%For any smooth manifold $M$ and Lie algebra $\fg$ the pair $(\bZ_n(\fg), \bU_n (\fg))$ define a constructible factorization algebra on the $(n+1)$-manifold with boundary $M \times \RR_{\geq 0}$.
%When $M = \RR^n$, this is a model for the algebra $(\fZ_n(\fg), \UU_n(\fg))$ over the $(n+1)$-dimensional Swiss cheese operad.
%\end{prp}
%
%\begin{proof}[Proof sketch]
%In the bulk manifold $M \times \RR_{>0}$ we place the 
%\end{proof}
